\documentclass{article}
\usepackage[margin=1in]{geometry}

\begin{document}

\noindent\textbf{Halil Kirisci}

\noindent \textbf{Birthplace:} Kayseri
\newline \textbf{Date of Birth:} 24.10.1980
\newline \textbf{Mobile Phone:} 0541 231 55 23
\newline \textbf{E-Mail:} halilkirisci@gmail.com
\newline \textbf{Linkedin:} https://www.linkedin.com/in/halil-kirisci-9a450763/



\noindent \textbf{Address: }
Eryaman 3.etap Ata Mah. 3752 Sk.
\newline Atapark Evleri Sitesi A Blok no:6/19
\newline Yenimahalle / ANKARA

\noindent \textbf{Marital Status:} Married since  2011
\newline \textbf{Military Status:} Discharged
\newline \textbf{Driving License:} B (1999)
\newline \textbf{Educational Background:} Computer Engineering (Graduate) | Forensic Master

\section*{Educational Background}

\noindent \textbf{High School (10.1992- 06.1999)}
\newline Anatolian Imam Hatip High School
\newline \textit{Numerical Information -- Turkish Education}

\noindent \textbf{University (10.2001 - 06.2002)}
\newline Mersin University
\newline \textit{School of Computer and Technology, Computer Programming -- Turkish Education}

\noindent \textbf{University (10.2003 - 01.2007)}
\newline Near East University
\newline \textit{Faculty of Computer Sciences, Computer Engineering -- English Education
}
\noindent \textbf{Master's Degree (09.2013 - 02.2015)}
\newline Gazi University
\newline \textit{Institute of Informatics, Forensic Informatics -- Turkish Distance Education}

\section*{Work Experience}

\noindent \textbf{PASIFIK (09.2002 - 08.2003)}
\newline Pasifik Advertising and Promotional Products Ind. Trade Ltd. Co. (KAYSERI)
\newline Design Element
\newline \textit{I worked as a graphic designer. I used Photoshop, Freehand programs on Mac OS systems, and also made web designs with flash; I provided remote active support to the company until 2008.}

\noindent \textbf{CYBERSOFT (01.2008 - 04.2009)}
\newline Cybersoft Information Technologies Ltd. Co. (ANKARA)
\newline \textit{I was involved in Module Development and Regulation with the Java language in the EVDO (Electronic Tax Office Automation) Project, which is a Finance Program within the Revenue Administration.}

\noindent \textbf{DESIGN SOFTWARE (09.2009 -- 09.2010)}
\newline Dizayn Software Consulting Ltd. Co. (ANKARA)
\newline \textit{As a Logo Partner company, I developed software integrated with Logo Business Package Systems and software related to the databases of other different software used by the company, using C\# language in Visual Studio 2008.}
\newline Abdulkadir Ozcan AS - Dealer Web Order System - Customer Tracking System
\newline ISLER BOOKSTORES Corporate Book Sales Website Dealer Web Order System

\noindent \textbf{CYBERSOFT}
\newline Cybersoft Information Technologies Ltd. Co. (ANKARA)
\newline Software Specialist (10.2010 -- 06.2011)
\newline \textit{Webservices software for EVDO3 (Electronic Tax Office Automation), E-Invoice, E-Seizure Projects in the Software Department of the company with Java language.}

\noindent \textbf{PRIME MINISTRY GENERAL DIRECTORATE OF PRESS, PUBLICATION AND INFORMATION}
\newline \textbf{Analyst (06.2011 - 06.2014)}
\newline \textit{I served as a Project Manager and Software Specialist on software and systems in the Archive and Information Processing Branch. (State Information System, Byegm Intranet, Accreditation System, Management Information System)}
\newline \textbf{Engineer (06.2014 - 07.2018)}
\newline \textit{I served as a Project Manager and Software Specialist on software and systems in the Archive and Information Processing Branch. (State Information System, Byegm Intranet, Press Card Application System, Management Information System)}

\noindent \textbf{Presidency of Communications}
\newline Engineer (07.2018 - ...)
\newline \textit{I served as a Project Manager and Software Specialist on software and systems in the Information Processing Department Branch. (State Information System, Byegm Intranet, Press Card Application System, Management Information System, CIMER)}

Because of Goverment Job can not use public sharement

\section*{Foreign Language}

\noindent English [Reading: 9 Writing: 9 Speaking: 7]

\section*{Computer Skills}

\noindent Programming Languages: Java, Asp.Net Core MVC (C\#, Visual Basic), React, ReactNative, Expressjs, Php, Ajax, CSS
\newline Databases: Oracle, MSSQL, MYSQL, Sybase, Firebird
\newline Software Packages: Office (Word, Excel, PowerPoint, FrontPage, Access) - Macromedia (Flash (Actionscript), Dreamweaver, FreeHand) - Adobe (PhotoShop, Flash, Dreamveawer)
\newline Operating Systems: Windows, Mac OS, Linux(Ubuntu, Centos)

\end{document}